%-------------------------------------
% LaTeX Resume for Software Engineers
% Author : Leslie Cheng
% License : MIT
%-------------------------------------

\documentclass[letterpaper,12pt]{article}[leftmargin=*]

\usepackage[empty]{fullpage}
\usepackage{enumitem}
\usepackage{ifxetex}
\ifxetex
  \usepackage{fontspec}
  \usepackage[xetex]{hyperref}
\else
  \usepackage[utf8]{inputenc}
  \usepackage[T1]{fontenc}
  \usepackage[pdftex]{hyperref}
\fi
\usepackage{fontawesome5}
\usepackage[sfdefault,light]{FiraSans}
\usepackage{anyfontsize}
\usepackage{xcolor}
\usepackage{tabularx}

%-------------------------------------------------- SETTINGS HERE --------------------------------------------------
% Header settings
\def \fullname {Thong Le Hoang}
\def \subtitle {Software Engineer}

% \def \linkedinicon {\faLinkedin}
% \def \linkedinlink {https://linkedin.com/in/dwight-schrute/}
% \def \linkedintext {/dwight-schrute}

\def \phoneicon {\faPhone}
\def \phonetext {+84-347-023-047}

\def \emailicon {\faEnvelope}
\def \emaillink {mailto:thongle0905@gmail.com}
\def \emailtext {thongle0905@gmail.com}

\def \addressicon {\faHome}
\def \addresstext {Ho Chi Minh, Viet Nam}

% \def \githubicon {\faGithub}
% \def \githublink {https://github.com/dwight-schrute}
% \def \githubtext {/dwight-schrute}

% \def \websiteicon {\faGlobe}
% \def \websitelink {https://google.com/}
% \def \websitetext {dwightschrute.com}

\def \headertype {\doublecol} % \singlecol or \doublecol

% Misc settings
\def \entryspacing {5pt}

\def \bulletstyle {\faAngleRight}

% Define colours
\definecolor{primary}{HTML}{000000}
\definecolor{secondary}{HTML}{0D47A1}
\definecolor{accent}{HTML}{263238}
\definecolor{links}{HTML}{1565C0}

%------------------------------------------------------------------------------------------------------------------- 

% Defines to make listing easier
\def \linkedin {\linkedinicon \hspace{3pt}\href{\linkedinlink}{\linkedintext}}
\def \phone {\phoneicon \hspace{3pt}{ \phonetext}}
\def \address {\addressicon \hspace{3pt}{ \addresstext}}
\def \email {\emailicon \hspace{3pt}\href{\emaillink}{\emailtext}}
\def \github {\githubicon \hspace{3pt}\href{\githublink}{\githubtext}}
\def \website {\websiteicon \hspace{3pt}\href{\websitelink}{\websitetext}}

% Adjust margins
\addtolength{\oddsidemargin}{-0.55in}
\addtolength{\evensidemargin}{-0.55in}
\addtolength{\textwidth}{1.1in}
\addtolength{\topmargin}{-0.6in}
\addtolength{\textheight}{1.1in}

% Define the link colours
\hypersetup{
    colorlinks=true,
    urlcolor=links,
}

% Set the margin alignment 
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%-------------------------
% Custom commands

% Sections
\renewcommand{\section}[2]{\vspace{5pt}
  \colorbox{secondary}{\color{white}\raggedbottom\normalsize\textbf{{#1}{\hspace{7pt}#2}}}
}

% Entry start and end, for spacing
\newcommand{\resumeEntryStart}{\begin{itemize}[leftmargin=2.5mm]}
\newcommand{\resumeEntryEnd}{\end{itemize}\vspace{\entryspacing}}

% Itemized list for the bullet points under an entry, if necessary
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=4.5mm]}
\newcommand{\resumeItemListEnd}{\end{itemize}}

% Resume item
\renewcommand{\labelitemii}{\bulletstyle}
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

% Entry with title, subheading, date(s), and location
\newcommand{\resumeEntryTSDL}[4]{
  \vspace{-1pt}\item[]
    \begin{tabularx}{0.97\textwidth}{X@{\hspace{60pt}}r}
      \textbf{\color{primary}#1} & {\firabook\color{accent}\small#2} \\
      \textit{\color{accent}\small#3} & {\firabook\color{accent}\small#4} \\
    \end{tabularx}\vspace{-6pt}
}

% Entry with title and date(s)
\newcommand{\resumeEntryTD}[2]{
  \vspace{1pt}\item[]
    \begin{tabularx}{0.97\textwidth}{X@{\hspace{60pt}}r}
      \textbf{\color{primary}#1} & {\firabook\color{accent}\small#2} \\
    \end{tabularx}\vspace{-6pt}
}

% Entry for special (skills)
\newcommand{\resumeEntryS}[2]{
  \item[]\small{
    \textbf{\color{primary}#1 }{ #2 \vspace{-6pt}}
  }
}

% Double column header
\newcommand{\doublecol}[6]{
  \begin{tabularx}{\textwidth}{Xr}
    {
      \begin{tabular}[c]{l}
        \fontsize{35}{45}\selectfont{\color{primary}{{\textbf{\fullname}}}} \\
        {\textit{\subtitle}} % You could add a subtitle here
      \end{tabular}
    } & {
      \begin{tabular}[c]{l@{\hspace{1.5em}}l}
        {\small#4} & {\small#1} \\
        {\small#5} & {\small#2} \\
        {\small#6} & {\small#3}
      \end{tabular}
    }
  \end{tabularx}
}

% Single column header
\newcommand{\singlecol}[6]{
  \begin{tabularx}{\textwidth}{Xr}
    {
      \begin{tabular}[b]{l}
        \fontsize{35}{45}\selectfont{\color{primary}{{\textbf{\fullname}}}} \\
        {\textit{\subtitle}} % You could add a subtitle here
      \end{tabular}
    } & {
      \begin{tabular}[c]{l}
        {\small#1} \\
        {\small#2} \\
        {\small#3} \\
        {\small#4} \\
        {\small#5} \\
        {\small#6}
      \end{tabular}
    }
  \end{tabularx}
}

\begin{document}
%-------------------------------------------------- BEGIN HERE --------------------------------------------------

%---------------------------------------------------- HEADER ----------------------------------------------------

\headertype{\linkedin}{\github}{\website}{\phone}{\email}{\address} % Set the order of items here
\vspace{10pt} % Set a negative value to push the body up, and the opposite

%-------------------------------------------------- PROGRAMMING SKILLS -------------------------------------------------
\section{\faChartLine}{Skills}
 \resumeEntryStart
  \resumeEntryS{Scripting language } {Typescript, NodeJS, Bash script, Python, Groovy}
  \resumeEntryS{Programming language } {Java, C++}
    \resumeEntryS{IaC and Automation } {Terraform, Ansible, Packer, Puppet}
  \resumeEntryS{Visualization and orchestration } {Docker, ECS, EKS/AKS (Kubernetes)}
  \resumeEntryS{CICD } {GitHub Action, Jenkins, Gitlab CI, Harness, ArgoCD}
  \resumeEntryS{Database } {PostgreSQL, Redis}
  \resumeEntryS{Cloud provider } {AWS: EKS, ECS, RDS, ElastiCache, S3, Lambda, IAM, R53, AWS Config, SNS...; Azure \textit{(basic)}}
  \resumeEntryS{SDLC } {Agile, V-module, workflow in ServiceNow}
  \resumeEntryS{Communication } {English}
 \resumeEntryEnd

%-------------------------------------------------- EXPERIENCE --------------------------------------------------
\section{\faBriefcase}{Experience}

  \resumeEntryStart
    \resumeEntryTSDL
      {AXON}{Oct 2024 -- Present}
      {Platform Engineer Contractor}{}
    \resumeItemListStart
      \resumeItem {\textbf{Set up staging GH Enterprise Server} then synchronize with Prod for verifying upgrading new version using \textit{Terraform and Puppet}.}
      \resumeItem {Built, patched and upgraded images for GH runners, TeamCity agents (both Windows and Linux) using \textit{Packer, Ansible and Docker}.}
      \resumeItem {Developed GH Actions such as one same as \textbf{Release-please but supports both semver, calver}; one showing \textbf{changes between deploying and running K8s Helm/Kustomize resources} in \textit{Typescript}.}
      \resumeItem {Wrote End-to-End tests for GH Actions.}
      \resumeItem {Significantly \textbf{reduce 85\% run duration and 40\% fetched artifacts size} of a GH Action by optimizing Git operations.}
      \resumeItem {Customized \textit{Helm chart} for deploying GH runners at Enterprise level using \textit{ArgoCD}.}
      \resumeItem {Created dashboard, alerts for TeamCity with custom metrics in \textit{Go and Prometheus, Cortex, Grafana} stack.}
      \resumeItem {Wrote documentations from platform view fully covering users, operators, maintainers and from proposal, design to implementation, release.}
      \resumeItem {On-call and troubleshoot support in Prod.}
      \resumeItem {Flexibly applied \textit{GH Copilot and ChatGPT} to wide area from coding to troubleshooting incidents, reviewing PRs, auto chatbot.}
    \resumeItemListEnd
  \resumeEntryEnd

  \resumeEntryStart
    \resumeEntryTSDL
      {NAB INNOVATION CENTRE VIETNAM}{Mar 2022 -- July 2024}
      {DevOps engineer cums Backend developer}{}
    \resumeItemListStart
      \resumeItem {Wrote auto jobs for repetitive processes such as Flyway migration, renewing certs, comparing deployments between envs... by using Bash \textit{script, Groovy, Python}.}
      \resumeItem {Developed a tool to gather info and verify configurations, help to \textbf{reduce almost 90\% wrong configurations} before releasing using \textit{schema-validator in NodeJS}.}
      \resumeItem {Wrote a tool interacting with Harness APIs for bulk triggering builds, deployment, smoke testing after deployment; help to reduce Click-Ops deployment \textbf{from 45m to less than 10m} by using \textit{NodeJS}.}
      \resumeItem {\textbf{Imported manually created AWS resources} into \textit{Terraform} code; govern permissions, protect rules, settings in GitHub via \textit{Terraform}.}
      \resumeItem {Onboarded services to \textit{ECS, EKS}, customize K8s and Jenkins resources based on configurations exposed from Platform team.}
      \resumeItem {Setup AppDynamic dashboard.}
      \resumeItem {\textbf{L3 support}, troubleshooted, coordinated with multi stakeholders (Aus DevOps, Product Owners, Release Train Engineer, Tech Leads...) to resolve incidents in Prod.}
      \resumeItem {Kept compliant about securities, vulnerabilities}
      \vspace{1pt}\small{
        \newline{Integrated security tools in CI: \textit{SonarQube (Code quality), Checkmarx (SAST), SonaType (SCA), Prisma (CSS), Snyk}...}
        \newline{Patched CVE configurations in Linux.}
      }\vspace{-1pt}
      \resumeItem {.}
      \vspace{-10pt}\resumeItem {Developed REST apis to support bankers managing debts/facilities, entities, covenants... of wholesales, enterprises with \textbf{blackbox tests to cover golden scenarios and 90\% code coverage unit tests} using Java, Spring boot.}
      \resumeItem {Enhanced API performance \textbf{from more than 10s to less than 3s}.}
    \resumeItemListEnd
    \textbf{\color{primary}\small#Achievement: }{\small#Outstanding performance 2023}
  \resumeEntryEnd

% \newpage
  \resumeEntryStart
    \resumeEntryTSDL
      {INCEPTION LABS}{Aug 2020 -- Feb 2022}
      {DevOps engineer}{}
    \resumeItemListStart
      \resumeItem {Managed users and permission, set up and configured Nginx, Systemd, ipTables... in Linux using \textit{Ansible}.}
      \resumeItem {\textbf{Wrote CICD} to build, run unit test, \textbf{deploy services to both Windows and Linux instances}... using \textit{GitlabCI}.}
      \resumeItem {Created automation jobs in \textit{Rundeck} to handle renew certs, delete long-time unused Artifactory, extract MongoDB data then upload to S3 for reports... wrote by \textit{Bash script}.}
      \resumeItem {\textbf{Set up high availability environment} in AWS to prepare for disaster recovery.}
      \resumeItem {L3 support, troubleshoot Prod issues.}
      \resumeItem {Crawled data, interact from/with websites via api, websocket, RabbitMQ with multi-threading \textit{Java}.}
    \resumeItemListEnd
  \resumeEntryEnd


  \resumeEntryStart
    \resumeEntryTSDL
      {ROBERT BOSCH ENGINEERING AND BUSINESS SOLUTIONS VIETNAM}{Apr 2018 -- July 2020}
      {Embedded developer}{}
    \resumeItemListStart
      \resumeItem {Developed communication (ComVeh, ComDia) in vehicle for Huyndai, Suzuki, Nissan using embedded C.}
      \resumeItem {Modified platform scripts to generate business desired code.}
      \resumeItem {Scheduled jobs in real time OS.}
      \resumeItem {Worked with V-model SDLC.}
    \resumeItemListEnd
  \resumeEntryEnd

  %-------------------------------------------------- EDUCATION --------------------------------------------------
\section{\faGraduationCap}{Education}
  \resumeEntryStart
    \resumeEntryTSDL
      {UNIVERSITY OF TECHNOLOGY (HCMUT)}{2013 -- 2018}
      {Major: Control engineering and Automation}{\vspace{5pt}}
      \textit{\color{accent}\small#GPT: 7.37/10.0}
    \resumeEntryTSDL
      {TIEN GIANG GIFTED HIGH SCHOOL}{2010 -- 2012}
      {Major: Information Technology}{}
\resumeEntryEnd


%-------------------------------------------------- CERTIFICATIONS --------------------------------------------------
\section{\faAward}{Certifications}
  \resumeEntryStart
    \resumeEntryTD
      {AWS Certified SysOps Administrator - Associate}{Upcoming in May 2024}
  \resumeEntryEnd
  \vspace{-20pt}
  
  \resumeEntryStart
    \resumeEntryTD
      {AWS Certified Cloud Practitioner}{Apr 2023}
  \resumeEntryEnd
  \vspace{-20pt}
  
  \resumeEntryStart
    \resumeEntryTD
      {TOEIC Certificate with score 690}{Jun 2018}
  \resumeEntryEnd

%-------------------------------------------------- ACTIVITIES --------------------------------------------------
\section{\faWalking}{Activities}
  \resumeEntryStart
    \resumeEntryTD
      {ONSITE IN INDIA}{Nov 2019 -- Jan 2020}
    \resumeItemListStart
      \resumeItem {Working onsite to India in main developer role in ComVeh Hyundai.}
    \resumeItemListEnd
  \resumeEntryEnd
  \vspace{-20pt}
  
  \resumeEntryStart
    \resumeEntryTD
      {HCMUT}{2013 -- 2018}
    \resumeItemListStart
      \resumeItem {Wiring, maintain electrical system for people in Green Summer campaign.}
      \resumeItem {Become a member of Pay It Forward club - an electrical electronics club.}
    \resumeItemListEnd
  \resumeEntryEnd

\end{document}